Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-17 talk/vmil2012/paper.tex
a note

* High level handling of resumedata
   * trade-off fast tracing v/s memory usage
   * creation in the frontendÂ
   * optimization
   * compression
   * interaction with optimization
   * tracing and attaching bridges and throwing away resume data
   * compiling bridges

@@

Code generation consists of two passes over the lists of instructions, a
backwards pass to calculate live ranges of IR-level variables and a forward one
to emit the instructions. During the forward pass IR-level variables are
assigned to registers and stack locations by the register allocator according to
the requirements of the to be emitted instructions. Eviction/spilling is
performed based on the live range information collected in the first pass. Each
IR instruction is transformed into one or more machine level instructions that
implement the required semantics.  Guards instructions are transformed into
fast checks at the machine code level that verify the corresponding condition.
In cases the value being checked by the guard is not used anywhere else the
guard and the operation producing the value can merged, reducing even more the
overhead of the guard.

>>>>

* High level handling of resumedata
   * trade-off fast tracing v/s memory usage
   * creation in the frontend
   * optimization
   * compression
   * interaction with optimization
   * tracing and attaching bridges and throwing away resume data
   * compiling bridges

@@

Code generation consists of two passes over the lists of instructions, a
backwards pass to calculate live ranges of IR-level variables \cfbolz{doesn't the backward pass also remove dead instructions?} and a forward one
to emit the instructions. During the forward pass IR-level variables are
assigned to registers and stack locations by the register allocator according to
the requirements of the to be emitted instructions. Eviction/spilling is
performed based on the live range information collected in the first pass. Each
IR instruction is transformed into one or more machine level instructions that
implement the required semantics.  Guards instructions are transformed into
fast checks at the machine code level that verify the corresponding condition.
In cases the value being checked by the guard is not used anywhere else the
guard and the operation producing the value can merged, reducing even more the
overhead of the guard.
